\documentclass{article}

\begin{document}
Design document for developed game with overall plan of modules of game.

\section{Introduction}
Game is 2D and based on cubes (technically squares). Main character is a cube with
various properties and abilities.

\section{Aim}
Aim of this project is to improve C++ knowledge, software engineering and teamwork skills.
This is short list of main programming features being practiced.

\begin{itemize}
    \item{OOP}
    \item{Inheritance}
    \item{STL}
    \item{Templates}
    \item{Exceptions}
    \item{Namespaces}
\end{itemize}

\section{Ideas}
Main character cube can equip different abilities on each side. Cubes can change colour,
size and bosses can dissasemble into tetrahedra (triangles in 2D). Dr X's will
be final boss. Every level is build solely from cubes (can be extended to spheres, \dots)
and they can react on player actions, e.g. cube shrinks every time player touches it.

\section{Technology}
Programming language used is C++ as it is one of the goals of this project to practice
this particular language. Initially, OpenGL is used to render cubes on screen, however
it should be possible to replace it with ray tracing methods if desired.
GLFW will provide low overhead OpenGL context.

OpenGL version can be either set on 4.4 or 3.3, this will be decided before embarking
on coding. Also, the ES version can be considered to ease portability to mobile devices.

Public github repository is used to track code changes.

\section{Design}
Game will have main loop with three main stages {\em input handling}, {\em physics},
{\em rendering}.

\subsection{Input Handling}
This stage should correctly capture key press and mouse clicks and update properties
of objects acted on.

\subsection{Physics}
Update position of every object by adding small step. Handling of variable framerate
was not discussed, for start, the framerate is fixed on 60 FPS.

\subsection{Rendering}
Last stage of main loop where visibility is tested and object are rendered on screen.


\section{Iteration 0}
Basic game mechanics should be implemented. This includes key capture, side movement
of cube on plane and rendering.


\end{document}
